Quantum Pseudo-Telepathy

### 2023-06-06 paper/main.tex
initial draft of quantum sol example

\newtcbtheorem{tcbexample}{Example}{
  colback=gray!15,
  colbacktitle=gray!15,
  coltitle=red!75!black,
  fonttitle=\bfseries,
  detach title,
  before upper={\tcbtitle},
  separator sign none,
  description delimiters={(}{). }
}{ex}

@@

  {\renewcommand{\arraystretch}{2}
    \begin{figure}[H]
      \centering
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
            \hhline{---}[
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
          \end{array}\]
        \caption{Initially, Alice and Bob agree that Bob shall fill the
          first column with \(\{-1, -1, -1\}\). Based on this choice,
          Alice decides to fill all of her rows with
          \(\{-1, -1, +1\}\).}
      \end{subfigure}
      \hfill{}
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|*{3}{>{\quad\columncolor{gray!50}}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & \cellcolor{red!80!black!55}\pm 1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
          \end{array}\]
        \caption{Bob has to fill the second column with \(-1\)'s, to match
          Alice's choice. He should also match Alice's choice for each
          cell of the third column, but he cannot, for the product of
          the column must be \(-1\).}
      \end{subfigure}
      \caption{One possible classical deterministic strategy for the Magic
        Square game. Following this predefined strategy, Alice and Bob
        lose when assigned, respectively, the first row and third column,
        but win in any other scenario. That is, their probability of
        winning a round is \(\nicefrac{8}{9}\). Gray cells are entries for
        which Alice's and Bob's choices agree.\label{fig:classical}}
    \end{figure}}
\end{tcbexample}

@@

>>>>

\newtcbtheorem{tcbexample}{Example}{
  boxrule=0.15mm,
  colback=gray!15,
  colbacktitle=gray!15,
  coltitle=red!50!black,
  fonttitle=\bfseries,
  detach title,
  before upper={\tcbtitle},
  separator sign none,
  description delimiters={(}{). }
}{ex}

@@

  {\renewcommand{\arraystretch}{2}
    \begin{figure}[H]
      \centering
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
          \end{array}\]
        \caption{Initially, Alice and Bob agree that Bob shall fill the
          first column with \(\{-1, -1, -1\}\). Based on this choice,
          Alice decides to fill all of her rows with
          \(\{-1, -1, +1\}\).}
      \end{subfigure}
      \hfill{}
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|*{3}{>{\quad\columncolor{gray!50}}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & \cellcolor{red!80!black!55}\pm 1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
          \end{array}\]
        \caption{Bob has to fill the second column with \(-1\)'s, to match
          Alice's choice. He should also match Alice's choice for each
          cell of the third column, but he cannot, for the product of
          the column must be \(-1\).}
      \end{subfigure}
      \caption{One possible classical deterministic strategy for the Magic
        Square game. Following this predefined strategy, Alice and Bob
        lose when assigned, respectively, the first row and third column,
        but win in any other scenario. That is, their probability of
        winning a round is \(\nicefrac{8}{9}\). Gray cells are entries for
        which Alice's and Bob's choices agree.\label{fig:classical}}
    \end{figure}}
\end{tcbexample}

@@

\begin{tcbexample}{Quantum Solution}{quantum-sol}
  Suppose that Charlie assigns the first row to Alice. To decide the
  value of the first cell, she (based on the \(3 \times 3\) grid she
  and Bob have prepared) measures the observable \(I \otimes Z\)
  on her two qubits. The possible outcomes are
  \begin{equation}
    \label{eq:outcomes-1r}
    \operatorname{Out}((I \otimes Z)_{A} \otimes (I \otimes I)_{B}) =
    \begin{cases}
      +1, \text{ proj. onto } \{\ket{i0jk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2} \\
      -1, \text{ proj. onto } \{\ket{i1jk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2}, \\
    \end{cases}
  \end{equation}
  where the subscript \(A1\) denotes the state after Alice's first
  measurement. Suppose that Alice has observed \(+1\). Notice that
  only two of the components of the \(+1\)-eigenspace are seen in the
  initial state \(\ket{\psi}\): \(\ket{0000}\) and
  \(\ket{1010}\). Therefore, \(\ket{\psi}\) collapses to
  \begin{equation}
    \ket{\psi}_{A1} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}).
  \end{equation}
  For the second cell, Alice measures the observable \(Z \otimes I\),
  whose possible outcomes are
    \begin{equation}
    \label{eq:outcomes-1r}
    \operatorname{Out}((Z \otimes I)_{A} \otimes (I \otimes I)_{B}) =
    \begin{cases}
      +1, \text{ proj. onto } \{\ket{0ijk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2} \\
      -1, \text{ proj. onto } \{\ket{1ijk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2}. \\
    \end{cases}
  \end{equation}
  Suppose, now, that Alice has observed the outcome \(-1\). Notice that
  only one component of the \(-1\)-eigenspace is seen in the state
  \(\ket{\psi}_{A1}\). Hence, the state collapses to
  \begin{equation}
    \ket{\psi}_{A2} =  \ket{1010}.
  \end{equation}
\end{tcbexample}
